---
title: "Music Insights"
author: "Brenndan Olson"
output:
  html_document:
    df_print: paged
---

##First, we need tidyverse to handle data importing and wrangling, and then read in the survey and preferences data frames

```{r}
library(tidyverse)

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

#nrow(preferences)
#colnames(preferences)
```

##Now we are going to changle column names of survey to be easier to use, by getting rid of the spaces

```{r}
colnames(survey)[colnames(survey)=="Timestamp"] <- "time_submitted"
colnames(survey)[colnames(survey)=="What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey)=="First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"
colnames(survey)[colnames(survey)=="Sex"] <- "sex"
colnames(survey)[colnames(survey)=="Major"] <- "academic_major"
colnames(survey)[colnames(survey)=="Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey)=="Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey)=="Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey)=="Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey)=="Song"] <- "favorite_song"
colnames(survey)[colnames(survey)=="Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
```

##Getting the libraries to help create clean and tidy data
```{r}
library(dplyr)
library(tidyr)
```
##We are going to transform the two current tables into four: person, favorite_song, ratings, and musical_talents(later)
```{r}
person <- dplyr::tibble(time_submitted = survey$time_submitted,pseudonym_generator = survey$pseudonym_generator, pseudonym = survey$pseudonym, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, year_born = survey$year_born)
favorite_song <- dplyr::tibble(pseudonym = survey$pseudonym, favorite_song_artist = survey$favorite_song_artist, favorite_song = survey$favorite_song, favorite_song_link = survey$favorite_song_link)
ratings <- preferences
ratings <- tidyr::gather(ratings,"artist_song","rating",3:ncol(preferences))
colnames(ratings)[colnames(ratings) == "Timestamp"] <- "time_submitted"
```

##We are going to fix the time_submitted column on person and ratings to be more universal

```{r}
library(readr)
person$time_submitted <- as.POSIXlt(parse_datetime(survey$time_submitted,"%m/%d/%y %H:%M",na=c("","NA")))
ratings$time_submitted <- as.POSIXlt(parse_datetime(preferences$time_submitted,"%m/%d/%y %H:%M",na=c("","NA")))

```